---
title: NEUROCOGNITIVE EXAMINATION
author: "Joey Trampush"
format:
  neuropsych-report: default
---

```{r}
#| label: setup
#| include: false
# knitr::opts_knit$set(width = 50)
options(digits = 1, warnPartialMatchArgs = FALSE)
options(knitr.kable.NA = "--")
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
knitr::knit_hooks$set(optipng = knitr::hook_optipng)
# Fix subfigs for rmarkdown -> latex
if (identical(knitr:::pandoc_to(), "latex")) {
  knitr::knit_hooks$set(plot = knitr::hook_plot_tex)
}
```


```{=typst}
#v(2pt, weak: true)
*PATIENT NAME:* `r params$first_name` `r params$last_name`\
*DATES OF EXAM:* `r params$doe1`, `r params$doe2`\
```

# TESTS ADMINISTERED

- Comprehensive Neuropsychiatric Symptom and History Interview
- Conners' Adult ADHD Diagnostic Interview for DSM-IV (CAADID), Part I: History
- Conners' Adult ADHD Rating Scales--Observer Report: Long Version (CAARS--O:L)
- Comprehensive Executive Function Inventory Adult (CEFI Adult) Observer Form
- Advanced Clinical Solutions (ACS): Word Choice Test
- Dot Counting Test
- Wechsler Adult Intelligence Scale, 4th ed (WAIS-IV)
- Wechsler Individual Achievement Test, 4th ed (WIAT-4)
- Neuropsychological Assessment Battery, Screener (NAB):
  - Attention, Language, Memory, Spatial, and Executive Functions Modules
- NIH Executive Abilities: Measures and Instruments for Neurobehavioral Evaluation and Research (NIH EXAMINER):
  - Unstructured Task, Verbal Fluency, and Behavior Rating Scale
- California Verbal Learning Test, 3rd ed (CVLT-3), Brief Form
- Rey-Osterrieth Complex Figure Test (ROCFT)
- Trail Making Test
- Personality Assessment Inventory (PAI)

# NEUROBEHAVIORAL STATUS EXAM

{{< include _nse.qmd >}}

# NEUROCOGNITIVE FINDINGS

```{r}
#| label: make-neuropsych
#| include: false
library(tidyverse)
patient <- "Biggie"
data_path <- here::here(patient, "csv")
files <- dir(data_path, pattern = "*.csv")
neuropsych <-
  files |>
  purrr::set_names() |>
  purrr::map_df(
    ~ readr::read_csv(file.path(data_path, .), show_col_types = FALSE),
    na = c("", "NA", "--", "-"),
    .id = "filename"
  ) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::distinct() |>
  dplyr::mutate(z = qnorm(percentile / 100)) |>
  dplyr::mutate(domain = forcats::as_factor(domain)) |>
  dplyr::mutate(subdomain = forcats::as_factor(subdomain)) |>
  dplyr::mutate(narrow = forcats::as_factor(narrow)) |>
  dplyr::mutate(pass = forcats::as_factor(pass)) |>
  dplyr::mutate(verbal = forcats::as_factor(verbal)) |>
  dplyr::mutate(timed = forcats::as_factor(timed))
```

```{r}
#| label: subset-domains
# Subset neurocognitive data
neurocog <-
  neuropsych |>
  dplyr::filter(test_type == "npsych_test")
# domain
neurocog <-
  neurocog |>
  dplyr::group_by(domain, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_domain = mean(z), z_sd_domain = sd(z)) |>
  dplyr::ungroup()
# subdomain
neurocog <-
  neurocog |>
  dplyr::group_by(subdomain, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_subdomain = mean(z), z_sd_subdomain = sd(z)) |>
  dplyr::ungroup()
# narrow
neurocog <-
  neurocog |>
  dplyr::group_by(narrow, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_narrow = mean(z), z_sd_narrow = sd(z)) |>
  dplyr::ungroup()
# pass
neurocog <-
  neurocog |>
  dplyr::group_by(pass, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_pass = mean(z), z_sd_pass = sd(z)) |>
  dplyr::ungroup()
# verbal
neurocog <-
  neurocog |>
  dplyr::group_by(verbal, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_verbal = mean(z), z_sd_verbal = sd(z)) |>
  dplyr::ungroup()
# timed
neurocog <-
  neurocog |>
  dplyr::group_by(timed, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_timed = mean(z), z_sd_timed = sd(z)) |>
  dplyr::ungroup()

# Subset neurobehavioral data
neurobehav <-
  neuropsych |>
  dplyr::filter(test_type == "rating_scale")
# domain
neurobehav <-
  neurobehav |>
  dplyr::group_by(domain, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_domain = mean(z), z_sd_domain = sd(z)) |>
  dplyr::ungroup()
# subdomain
neurobehav <-
  neurobehav |>
  dplyr::group_by(subdomain, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_subdomain = mean(z), z_sd_subdomain = sd(z)) |>
  dplyr::ungroup()
# narrow
neurobehav <-
  neurobehav |>
  dplyr::group_by(narrow, .add = TRUE) |>
  dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_narrow = mean(z), z_sd_narrow = sd(z)) |>
  dplyr::ungroup()

# Subset validity data
validity <-
  neuropsych |>
  dplyr::filter(test_type %in% c("performance_validity", "symptom_validity"))
# domain
validity <-
  validity |>
  dplyr::group_by(domain, .add = TRUE) |>
  # dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_domain = mean(z), z_sd_domain = sd(z)) |>
  dplyr::ungroup()
# subdomain
validity <-
  validity |>
  dplyr::group_by(subdomain, .add = TRUE) |>
  # dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_subdomain = mean(z), z_sd_subdomain = sd(z)) |>
  dplyr::ungroup()
# narrow
validity <-
  validity |>
  dplyr::group_by(narrow, .add = TRUE) |>
  # dplyr::filter(!is.na(percentile)) |>
  dplyr::mutate(z_mean_narrow = mean(z), z_sd_narrow = sd(z)) |>
  dplyr::ungroup()
```

```{r}
#| label: write-neuro-data
readr::write_csv(neuropsych, here::here(patient, "neuropsych.csv"))
readr::write_csv(neurocog, here::here(patient, "neurocog.csv"))
readr::write_csv(neurobehav, here::here(patient, "neurobehav.csv"))
readr::write_csv(validity, here::here(patient, "validity.csv"))

## read
neuropsych <- readr::read_csv(here::here(patient, "neuropsych.csv"))
neurocog <- readr::read_csv(here::here(patient, "neurocog.csv"))
neurobehav <- readr::read_csv(here::here(patient, "neurobehav.csv"))
validity <- readr::read_csv(here::here(patient, "validity.csv"))
```

## Behavioral Observations

{{< include _behav_obs.qmd >}}

## Intelligence/General Ability

{{< include _iq_text.qmd >}}

{{< include _iq2.qmd >}}
